\documentclass[12pt,journal,compsoc]{IEEEtran}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}

\graphicspath{{images/}}



\title{WebStegFS Implementation}
\author{Ryne~Flores, Kyle~Gorak, David~Hart, Matthew~Sjoholm, LTC Timothy Nix \\ \IEEEmembership{Department of Electrical Engineering and Computer Science\\ United States Military Academy}}
\IEEEtitleabstractindextext{
\begin{abstract}
In 2007 Arati Baliga, Joe Kilian, and Liviu Iftode of Rutgers University presented the idea of a web based covert file system~\cite{Baliga2007}. The purpose of a web based covert file system is providing confidentiality and plausible deniability regarding the existence of files. The key components of a web based covert file system is hiding files within media using steganographic techniques using online file sharing for the purpose of collaboration~\cite{Baliga2007}. We implemented such a system, WebStegFS, as a prototype to develop the idea for a web based covert file system previously mentioned. Our prototype of the web based covert file system implements steganographic techniques to obfuscate an entire file system on a public file share site. By storing data in this manner, rather than within the application or on a users computer, we provide confidentiality and plausible deniability to both the users and the companies that manage these public file sharing sites. 
\end{abstract}}
\date{}

\begin{document}
\maketitle

\section{Introduction}

\IEEEPARstart{W}{e} continue to integrate technology more and more in our daily lives because of the convenience it provides to users. Users are becoming connected to the internet in multiple ways nearly everywhere they go. The majority of people interact with multiple forms of technology throughout each day. Some technologies we interact with collect data from our interaction. Also, the widespread use of social media makes it easier to find information about people. Technology, coupled with social media and other applications, can begin to paint a picture used to identify individuals with only non-identifiable information~\cite{VanDam2015}. Sometimes this data collection is used solely to advertise a product to you, but sometimes there are more nefarious means of data collection that lead to black mail, social engineering attacks, or worse. 

The means to store and share information in a covert manner not only serves multiple purposes, but also has various implications depending on how those means are used. There will be innovations designed with the good intentions, yet there will also usually be clever modifications of those designs for malicious intentions. Such examples would include freely expressing and sharing interests ranging from hobbies to religion and sexuality without fear of reprisal or being condemned. However, studies have shown that unethical behavior tends to dominate within the realm of anonymity~\cite{Guitton2013}.

This project is an application that allows users to share information in a covert manner that can provide plausible deniability to not only the users but also to the file sharing or social media site used to store the information. Plausible deniability is ``(The possibility of) denying a fact (especially a discreditable action) without arousing suspicion; the method of achieving this.''\cite{OxfordDictionary} Even if the existence of the file system is uncovered, the data should remain protected and confidential.  

The possibility and threat of cyber attacks on not only individuals but also various infrastructures that are connected to the Internet generates need to securing store information. Encryption is a powerful tool to maintain secrecy of sensitive data and is very important in various institutions such as the financial institution~\cite{Grover2004}. This tool is available to the everyone and will continue to play an important role of information security as not only technology becomes more advanced but also as individuals work to protect their sensitive information from public view on the Internet.

\section{Related Works}

\subsection{StegFS}
There are other projects and systems that have been released which offer users covert methods of sharing information. One such work is StegFS~\cite{Tan2003}.  The concept of StegFS is a designing a file system that contains protected directories which are hidden through the use encryption and steganography. To the extent that these protected directories would not be located or detected unless a password or access key is provided~\cite{Tan2003}. This implementation grants users plausible deniability to the existence of any information contained within those protected directories, yet these protected directories are still stored to an extent within the user's machine. All information used within WebStegFS will only be stored within RAM, thus it increases the security and plausible deniability benefits to users.

In StegFS the hidden files are identified and accessed through their own headers. The encryption is designed to hide the existence of this hidden files from anyone that does not possess the correct access key. StegFS uses the following three data structures to construct the hidden file system: 
\begin{itemize}
\item A link to an inode table that indexes all the data blocks in the file~\cite{Tan2003}
\item A signature that uniquely identifies the file~\cite{Tan2003}
\item A linked list of pointers to free blocks held by the file'~\cite{Tan2003}
\end{itemize}

This file system has been implemented in Linux kernel 2.4 and is available for public download~\cite{Tan2003}. Performance reports have shown that this StegFS implementation was on par with the native Linux file system on a multi-user environment~\cite{2003}.

%\subsection{Tor}

\subsection{CovertFS}
In 2007 three members of the Department of Computer Science from Rutgers' University provided the main concepts and basic outline for the implementation and design of a covert file system\cite{Baliga2007}.  To the best of our knowledge there has been no other implementation of the application described in Rutger's paper, and this project is our take at creating a working prototype which could later be used to develop a successful application or implementation of the covert file system.

CovertFS was a concept of a file system application that would allow users to covertly store and share files on media sharing websites, and where the application could interact with any web based media sharing site~\cite{Baliga2007}. This system was intended to provide complete confidentiality and plausible deniability not only to the users of this application but also to the online media sharing sites that users had covertly stored information on. CovertFS was to accomplish this through the use of advanced Steganography and by not allowing the application to store information on the user's local machine~\cite{Baliga2007}.

%Yet by entering the covert realm of the internet we are allowing our project to criticized on the ethics of it development in accordance with ACM code of Ethics and Professional Conduct\cite{Anderson1993}. Just as Tor is reviewed arguments are brought up against further development\cite{Guitton2013} so to may this project draw vast attention because of what it offers or means to malicious users and intentions.

\section{Design Overview}

In this section, we describe  the architecture of WebStegFS. The five components of WebStegFS that will be described are: the purpose of the web connection in WebStegFS, how the file system is established and operates, how the file system is mapped to photos, the Steganography that WebStegFS uses, and how the file system is encoded.

\input{webConnectionPart}

\input{FUSEpart}

\subsection{Mapping File System Data to Photos}

After the user is done using the file system on their local machine, the data stored within must be uploaded to the online file store. This is done by a three step process.
\begin{enumerate}
\item All data files are uploaded to the online file store, after being processed by the steganography class. The download URL for the uploaded data is stored in the file metadata, in the file system object.
\item The file system is encoded to a string. This includes all directory names, as well as file metadata, such as file names, creation date/time, and the URL at which the file data can be found.
\item The string object that holds all the file system information is sent to the steganography class to be encoded and uploaded. A URL is returned to access the file system at a later time.
\end{enumerate}
Through this process, all information related to the file system is stored in a string, making it available for future use.

\input{stegPart}

\section{Tails}

An implementation that would increase the flexibility and security of this project is developing the WebStegFS into the TAILS operating system and having it run as a bootable program through the a flash drive. The reason for this is because the TAILS operating system in and of itself offers various security measures to ensure a stable and functioning system. We are working to develop a working prototype where our WebStegFS is integrated in the TAILS operating system to further allow confidentality and plausible deniability to the users. 

\section{Future Work}
The current implementation of WebStegFS does not require user authentication to access the file system, it only requires the 6-character code of the file system image to access all files in the system. We use versioning (i.e. the current version of the file system uses this code, if a change is made then a new code will be generated and correspond to the new file system) in order to protect the information stored in the file system from being deleted--- WebStegFS does not ever delete images from the online file storage site, even though some sites allow it. 

An alternative approach could require a user to have an account with the WebStegFS database. This would take away the idea of plausible deniability, as every user would require some sort of entry in the database. However, it could add to the confidentiality of the file system, as only authenticated users would be able to access the data.Another possibility would be to add a simple password entry into the encryption suite. This could increase confidentiality, without removing plausible deniability.

\subsection{Encryption and Advanced Steganography Techniques}

Another future implementation worth looking into is the use of a more advanced steganographic technique. The purpose of this is to ensure the confidentiality and plausible deniability of the users by:
\begin{enumerate}
\item Ensuring that pictures being used to hide the information do not give tell-tale signs of modification
\item To increase the difficulty of steganographic tools discovering the encrypted pictures within the sea of publicly shared images within the file sharing site or social media site that the system it using to store the file system.
\end{enumerate}

There are many different kinds of steganographic techniques that assist in reducing the effectiveness of statistical analysis, recovery of data, and other methods of detection. [?] Other implementations of steganography do not use images at all, but rather encode data within other forms of media such as audio files or PDFs. Using a better steganographic technique in addition to encryption would increase confidentiality and plausible deniability [?]. 

\section{Conclusion}

WebStegFS is the implementation of the CovertFS concept. It is an application that allows users to store and share files covertly through the use of a media sharing site and allows plausible deniability to users and the media sharing sites that they use. It is a modular application that allows users to swap out and customize its various components to include: the type of steganography used, how it establishes a web connection and what media sharing site it uses, and the type of encryption that is used. 

\bibliographystyle{plain}
\bibliography{covertfsrefs}


\end{document}